### 2017-06-08 Paper/plos-latex-template/Supplemental.tex
updates

>>>>

\begin{table}[!ht]
\centering
\vspace{2.5 mm}
\begin{tabular}{|l| l| l|}
\hline
Name& nPIR & PPR \\
\hline
\hline
Ferrara N.	 & 46693 & 1.12 \\ 
Folkman J. & 23660 & 1.15 \\ 
Ullrich A. & 23034 & 1.46 \\ 
Jain R. & 15267 & 1.13 \\ 
Heldin C.	& 15148 & 1.21 \\ 
Druker B.	& 15088 & 1.16 \\ 
Schlessinger J.	& 14996 & 1.48 \\ 
Dvorak H.	 & 14230 & 1.13 \\ 
 Alitalo K.	& 13812 & 1.24 \\ 
 Slamon D. & 13587 & 1.46 \\ 
 Baselga J. & 12908 & 1.36 \\ 
 Kantarjian H. & 12029 & 1.17 \\ 
 Hicklin D.	 & 11775 & 1.17 \\ 
 Witte O. & 11449 & 1.08 \\ 
 Hanahan D. & 11072 & 1.19 \\ 
 Buchdunger E.	 & 11032 & 1.22 \\ 
 Risau W.	& 10950 & 1.24 \\ 
 Talpaz M.	 & 10713 & 1.13 \\ 
 Mendelsohn J.	 & 10534 & 1.54 \\ 
 Lydon N. & 9988 & 1.18 \\ 
 Goldman J. & 9927 & 1.11 \\ 
 Shibuya M. & 9639 & 1.21 \\ 
 Kitamura Y. & 9486 & 1.24 \\ 
 Waldmann H. & 9363 & 1.04 \\ 
 Kerbel R.	 & 9266 & 1.16 \\ 
   \hline
\end{tabular}
\vspace{2.5 mm}
\caption{
{\bf Elite Performers} Researchers with the highest nPIR scores in the network of 5 anti-cancer therapeutics are listed. Also shown for each researcher is their PIRpartitionRatio (PPR). The nPIR indicates influence across all five networks and the PPR provides an estimate of how this influence is partitioned across each of the five networks (Materials and Methods). This list and its ordering should be considered in the context of the data being analyzed and not interpreted as an absolute ordering of research excellence in the field.}
\label{table2}
\end{table}
